True Stellar Obliquity Distribution of Exoplanets

### 2022-11-15 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}[ht!]
    \script{hbm_istar.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/hbm_istar.pdf}
        \caption{Plot showing a bunch of random numbers.}
        \label{fig:hbm_istar}
    \end{centering}
\end{figure}

\begin{figure}
    \script{hbm_all.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/hbm_all.pdf}
        \caption{Plot showing a bunch of random numbers.}
        \label{fig:hbm_all}
    \end{centering}
\end{figure}

>>>>

\begin{figure}[ht!]
    \script{hbm_istar.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/hbm_istar.pdf}
        \caption{Hierarchical Bayesian model to infer \emph{true} stellar obliquity for planets with $\hat{i}_{\star}$ inferred from their rotation periods.}
        \label{fig:hbm_istar}
    \end{centering}
\end{figure}

\begin{figure*}
    \script{hbm_all.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/hbm_all.pdf}
        \caption{Hierarchical Bayesian model to infer \emph{true} stellar obliquity for all planets with sky-projected stellar obliquities measured.}
        \label{fig:hbm_all}
    \end{centering}
\end{figure*}
